surfing

### 2021-05-04 inst/surfing.Rmd
surfing

Of the 11 locations
in 2019, three competitions stand out as the waves at locations are
known for the size and power.

At these locations, judges score riding
inside the wave (“tubed”) higher than other turn or air style
manoeuvres.  The locations are Pipeline in Hawaii, Teahupo’o in Tahiti
and Margaret River in Western Australia.

```{r}
show <- function(filename){
  unlist(lapply(strsplit(readLines(filename)," "),paste,collapse=" "))
}					       
show("surfing_minimal.txt")
```

The first line shows that `Florence` came first, `Andre` second, and
so on.  We can convert this dataset into a Plackett-Luce likelihood
function as follows:

@@

f <- function(filename){
  o <- strsplit(readLines(filename)," ")
  H <- hyper2()
  for(v in o){H <- H + race(v)}
  return(H)
}

surfing <- f("surfing_minimal.txt")
pnames(surfing)
head(surfing)
```

>>>>

```{r}
head(read.table("players.txt",header=TRUE))
```

```{r}
o <- strsplit(readLines("wct.txt")," ")
jj <- unlist(lapply(o,paste,collapse=" "))
head(jj)
tail(jj)
```

The first line shows that, at one of the heats in `wct01`, `Colapinto`
came first, `Bailey` second, and `Wright` came third.  The last line
shows that, at `wct11`, `Ferreira` came first and `Medina` came
second.  We can convert this dataset into a Plackett-Luce likelihood
function as follows:

@@

surfing <- hyper2()
for(v in o){surfing <- surfing + race(v[-1])} # first entry is venue
summary(surfing)
```
